\documentclass[fleqn,10pt]{article}

\usepackage[left=2cm,right=2cm,
top=1.25cm,
bottom=0.5cm,%
headheight=11pt,%
letterpaper]{geometry}

\include{preamble}


\begin{document}
{\small
Daniel Correia\\
20 Silver Glen Boulevard\\
Collingwood, Ontario L9Z 1J9\\
Canada\\
(I have German citizenship and am eligible to work in the E.U.)}

\noindent
\noindent\makebox[\textwidth][c]{%
\begin{minipage}{0.8\textwidth}
	
\setlength{\parskip}{8pt}
\setlength{\parindent}{0.0mm}
	

Dear Recruiting Manager,


In regard to the position of "Software Developer for the Open Science Lab", kindly find my application enclosed. 
%
\begin{fquote}[U.N. ][Universal Declaration of Human Rights]
	Everyone has the right freely to participate in the cultural life of the
community, to enjoy the arts \textbf{and to share in scientific advancement and
its benefits.}\\
\end{fquote}

Having tried to pursue relatively "high-tech" projects in industry and academia, I am sensitive to the profound effects that access to scientific information can have on society. I have particular interest in developing systems that properly capture, retain, and freely supply scientific knowledge.

That said, my attempts at scientific documentation have been found wanting to date - I look forward to learning further best practices in this position.
\subsubsection*{Here is how my experience compares to the requirements of the position:}

\begin{quote}
Successfully completed university degree (Bachelor/FH-Diploma or Master/University-Diploma or equivalent) in a relevant field of study, preferably in computer science or a related field
\end{quote}

\cmark\ I have a B.Sc in Science from York University, with emphasis on courses in EE and CS.

\begin{quote}
Experience in software development in the environment of web-based applications (Java, JavaScript, Python)
\end{quote}

\cmark\ Some 5 years' experience and numerous projects in Python, a few months and several courses in Java and various web frameworks and template engines. Projects involving these technologies are detailed in the resume.

\ntilde\ Despite having used Javascript in a few projects, I am not competent in it yet.

\begin{quote}
High degree of self-organisation and independent working skills
Good communication skills

\end{quote}

\begin{quote}
Practical experience in the development and use of web services
\end{quote}

\begin{quote}
Knowledge of semantic web/linked data technologies (SPARQL, RDF)
\end{quote}
\xmark\ I have no such experience
\begin{quote}
Knowledge of version management systems based on Git - Knowledge of CI/CD workflows based on GitLab, Ansible and Docker
\end{quote}
\cmark I have used Git extensively and Docker briefly; little experience in CI/CD. 

Thanks for your time!

\end{minipage}}
%\newgeometry{textwidth=10cm,textheight=10cm}



\restoregeometry


\clearpage

\end{document}